---
title: "Stat Seminar Project Multiclass Model Building"
author: "Joe Coyne"
date: "`r Sys.Date()`"
output: word_document
---

First model - binary predictor -> 0 = first round exit (balanced 32 vs 32), 1 = other 
Second model - multiclass -> use ROC index instead of accuracy

```{r setup, include=FALSE}
library(tidyverse)
library(corrplot)
library(tidyselect)
library(caTools)
library(pROC)
library(caret)
library(tree)
library(keras)
library(tensorflow)
library(reticulate)
library(MASS)
library(car)
library(neuralnet)
library(multiROC)
```

```{r}
rmarkdown::render("Stat Seminar Project Binary Model Building.Rmd")
```

 * will probably have to deal with class imbalance issue
    - so many more teams (~300) have 0 postseason wins compared to the few (~30) who have 1 or more
    - starting with just the teams that made the NCAA tournament -> still class imbalance but smaller (only ~30 with       0 PostW)
    
### Removing Multicollinearity

```{r}
final_data <- multiclass_data %>% 
  dplyr::select(c(Wins, PostW, total_NumOT, total_FGM, total_OffReb, total_DefReb, total_Ast, total_Stl, total_Blk, total_PF, FTr, Three_PAr, TRB_percent, BLK_percent, TOV_percent))
# removed for multicollinearity

# cor(final_data %>% 
#       dplyr::select(-"PostW"))

# Assuming final_data contains your predictors and PostW
predictors <- final_data[, -which(names(final_data) == "PostW")]
scaled_predictors <- as.data.frame(scale(predictors, center = FALSE))
all_data_scaled <- cbind(final_data["PostW"], scaled_predictors)

# Assuming your_data is your tbl_df and model is your regression model
# Replace predictor1, predictor2, etc., with the actual names of your predictors
model_all_data <- polr(PostW ~ ., data = all_data_scaled)

# Calculate VIF
vif_values <- vif(model_all_data)
vif_values
```

```{r}
# initial_model_03_06_numeric <-  initial_model_03_06 %>% 
#   dplyr::select(-c(TeamID, Team_Name))  # removed for multicollinearity
# 
# # Convert non-numeric columns to numeric
# cor(initial_model_03_06 %>% 
#   dplyr::select(-c(PostW, TeamID, Team_Name, Losses, total_pts, total_FGA, total_FGA3, total_FTA)))
# 
# # Assuming initial_model_03_06_numeric contains your predictors and PostW
# predictors <- initial_model_03_06_numeric[, -which(names(initial_model_03_06_numeric) == "PostW")]
# scaled_predictors <- as.data.frame(scale(predictors, center = FALSE))
# initial_model_03_06_scaled <- cbind(initial_model_03_06_numeric["PostW"], scaled_predictors)
# 
# # Assuming your_data is your tbl_df and model is your regression model
# # Replace predictor1, predictor2, etc., with the actual names of your predictors
# model_03_06 <- polr(PostW ~ ., data = initial_model_03_06_scaled)
# 
# # Calculate VIF
# vif_values <- vif(model_03_06)
# vif_values
```


* does split maintain the same proportion of each category? 
* adjust F score and misc rate for 7 categories
* find examples of multi-category

## All Seasons

- just use all seasons data and not year segments

- when applying to just one season, use all but that season as training data, that season as testing data

** In the confusion matrices, not every value has a prediction. This is fine for initial model explorations, but will want to ensure each value has correct number of predictions when implementing on year by year basis (ex: champ and runner up with 1, final four but dont advance 2, ...)


#### Partitioning Data
```{r}
set.seed(123)
parts = createDataPartition(final_data$PostW, p = .5, list = F)
train = final_data[parts, ]
test = final_data[-parts, ]
```



```{r}
# set.seed(123)
# 
# # Identify levels of PostW
# postW_levels <- levels(final_data$PostW)
# 
# # Initialize empty data frames for train and test
# train <- data.frame()
# test <- data.frame()
# 
# # Set the proportion of observations to include for each level
# proportion_to_include <- 0.8
# 
# # For each level of PostW, select a proportion of observations for both train and test
# for (level in postW_levels) {
#   level_data <- final_data[final_data$PostW == level, ]
# 
#   # Calculate the number of observations to include for train and test
#   num_to_include <- round(nrow(level_data) * proportion_to_include)
# 
#   # Select observations for train without replacement
#   train_level <- level_data[sample(nrow(level_data), num_to_include, replace = FALSE), ]
#   train <- rbind(train, train_level)
# 
#   # Select remaining observations for test without replacement
#   test_level <- level_data[!(rownames(level_data) %in% rownames(train_level)), ]
#   test <- rbind(test, test_level)
# }
# 
# # Check if the sample size is less than the original data size for train
# if (nrow(train) < nrow(final_data)) {
#   # Randomly sample the remaining observations for train without replacement
#   remaining_train <- final_data[!(rownames(final_data) %in% rownames(train)), ]
#   remaining_train <- remaining_train[sample(nrow(remaining_train), size = nrow(final_data) - nrow(train), replace = FALSE), ]
#   train <- rbind(train, remaining_train)
# }
# 
# # Check if the sample size is less than the original data size for test
# if (nrow(test) < nrow(final_data)) {
#   # Randomly sample the remaining observations for test without replacement
#   remaining_test <- final_data[!(rownames(final_data) %in% rownames(test)), ]
#   remaining_test <- remaining_test[sample(nrow(remaining_test), size = nrow(final_data) - nrow(test), replace = FALSE), ]
#   test <- rbind(test, remaining_test)
# }
```


### Jackknife - LOOCV
LOOCV = leave one out cross validation

k-fold cross validation - jackknife --> leave one out (LOO)
```{r}
# Load libraries
library(caret)
library(MASS)
library(MLmetrics)

set.seed(123)  # Set seed for reproducibility

# Define the training control for cross-validation
ctrl <- trainControl(
  method = "cv",  # Cross-validation method ("cv" for k-fold, "LOOCV" for leave-one-out)
  number = 20,     # Number of folds or leave-one-out for LOOCV
  summaryFunction = multiClassSummary,  # For ordinal outcomes
  classProbs = TRUE,  # For probability estimates
  verboseIter = FALSE  # Display progress
)

# Specify the model
model_all_data_jk <- caret::train(
  PostW ~ .,
  data = train,
  method = "polr",  # Ordinal logistic regression
  trControl = ctrl
)

# Print the results
print(model_all_data_jk)


# Predictions
test$predictions_jk <- predict(model_all_data_jk, newdata = test, type = "prob")

test$predicted_class <- as.factor(colnames(test$predictions_jk)[max.col(test$predictions_jk)])

test$predicted_class <- factor(test$predicted_class, levels = levels(test$PostW))

confusion_matrix_jk <- confusionMatrix(test$predicted_class, test$PostW)

confusion_matrix_jk


# # Access additional information (e.g., confusion matrix, variable importance)
# confusionMatrix(model_all_data_jk)
# varImp(model_all_data_jk)
# 
# summary(model_all_data_jk)
```

```{r}
test$PostW <- factor(test$PostW, levels = levels(test$predicted_class))

pred_matrix_jk <- as.matrix(test$predictions_jk)

roc_jk <- multiclass.roc(test$PostW, pred_matrix_jk)
roc_jk
```
AUC: 0.6175


### Decision Tree
```{r}
# Check if levels of PostW appear more than once in the training data
table(train$PostW)

# specifying the CV technique which will be passed into the train() function later and number parameter is the "k" in K-fold cross validation
train_control = trainControl(method = "cv", number = 10, search = "grid")

## Customsing the tuning grid (ridge regression has alpha = 0)
multi_classification_Tree_Grid =  expand.grid(maxdepth = c(1,3,5, 7, 9))

# training a Regression model while tuning parameters (Method = "rpart")
tree_model = caret::train(PostW~., data = train, method = "rf", trControl = train_control)

# tree_model = caret::train(PostW~., data = train, method = "rpart", trControl = train_control, tuneGrid = multi_classification_Tree_Grid)

# summarizing the results
print(tree_model)

par(mar = c(0, 0, 0, 0))
plot(rpart(tree_model, data = final_data))
text(rpart(tree_model, data = final_data))

summary(rpart(tree_model, data = final_data))

#use model to make predictions on test data
pred_y = predict(tree_model, test)

# confusion Matrix
confusionMatrix(data = pred_y, test$PostW)
```
* may want to prune tree?

```{r, warning=FALSE}
pred_prob_tree <- predict(tree_model, test)

roc_tree <- multiclass.roc(test$PostW, pred_prob_tree)
roc_tree
```
AUC: 0.6488



### Stepwise Selection
```{r}
set.seed(2003)
null.polr <- polr(PostW~1, data=(train))
full.polr <- polr(PostW~., data=(train))
reg.step <- step(null.polr, scope=list(lowr=null.polr, upper=full.polr), direction = "both")
summary(reg.step)

reg.step_pred <- predict(reg.step, test, type = "class")

confusion_matrix_step <- table(reg.step_pred, test$PostW)

accuracy_step <- sum(diag(confusion_matrix_step)) / sum(confusion_matrix_step)

print(confusion_matrix_step)
cat("Accuracy:", accuracy_step, "\n")
```

```{r, warning=FALSE}
reg.step_pred <- as.ordered(reg.step_pred)
roc_curve_step <- multiclass.roc(test$PostW, reg.step_pred)
roc_curve_step
```
AUC: 0.5805


ANN
```{r}
# model_ann <- final_data %>% 
#   mutate(PostW = factor(PostW, levels = c("First.Round.Exit", "Round.of.Thirty.Two", "Sweet.Sixteen", "Elite.Eight", "Final.Four", "Runner.Up", "Champion"), labels = 0:6, ordered = T))
# 
# set.seed(123)
# parts_ann = createDataPartition(model_ann$PostW, p = .5, list = F)
# train = model_ann[parts_ann, ]
# test = model_ann[-parts_ann, ]
# 
# vars.ann <- attr(terms(reg.step), "term.labels") # extract variable names from bwd model
# 
# ## Standardization ##
# library(caret)
# ScaleParams <- preProcess(model_ann[parts, vars.ann], method=c("center", "scale"))
# model_ann <- model_ann %>% predict(ScaleParams, .)
# 
# x.train <- model_ann[parts, -ncol(model_ann)]
# y.train <- model_ann[parts,"PostW"]
# x.valid <- model_ann[-parts, -ncol(model_ann)]
# y.valid <- model_ann[-parts,"PostW"]
# 
# 
# library(tensorflow)
# library(keras)
# 
# set_random_seed(2003)
# ann <- keras_model_sequential() %>%
#   layer_dense(units = 8, activation = "tanh", input_shape = c(9)) %>%
#   # layer_dense(units = 21, activation = "tanh", input_shape = c(22)) %>%
#   layer_dense(units = 7, activation = "softmax")
# # last layer should be 7 units
# 
# 
# ann %>% compile(
#   loss = "sparse_categorical_crossentropy",
#   optimizer = "adam",
#   metrics = c("accuracy")
# )
# 
# 
# callbacks.list = list(
#   callback_model_checkpoint(filepath="ann_stat_sem_proj.h5",
#                             monitor = "val_loss",
#                             save_best_only = TRUE,
#   ))
# 
# 
# history <- ann %>% fit(
#   x= x.train,
#   y= y.train,
#   epochs = 40,
#   validation_data = list(x.valid,y.valid),
#   verbose = 1,
#   callbacks = callbacks.list
# )
# 
# 
# ann.select<- load_model_hdf5("ann_stat_sem_proj.h5")
```


        

```{r}
# library(neuralnet)
# 
# col_list_03_06 <- paste(c(colnames(initial_model_03_06_numeric)),collapse="+")
# col_list_03_06 <- paste(c("PostW~",col_list_03_06),collapse="")
# f_03_06 <- formula(col_list_03_06)
# 
# index_03_06 <- sample(1:nrow(initial_model_03_06_numeric),round(0.75*nrow(initial_model_03_06_numeric)))
# ann_train_03_06 <- initial_model_03_06_numeric[index_03_06,]
# ann_test_03_06 <- initial_model_03_06_numeric[-index_03_06,]
# 
# ann_test_03_06[, 1:12] <- lapply(ann_test_03_06[, 1:12], as.numeric)
# ann_test_03_06[, 1:12] <- scale(ann_test_03_06[, 1:12])
# 
# 
# nn1_03_06 = neuralnet(f_03_06, data=ann_train_03_06, hidden=3, act.fct = "logistic", linear.output =FALSE)
# result=compute(nn1_03_06, ann_test_03_06[,1:13])
```


```{r}
# numeric_vars_03_06 <- sapply(train2003_06, is.numeric)
# train_numeric_03_06 <- train2003_06[, numeric_vars_03_06]
# 
# # Assuming 'PostW' is a factor variable
# train2003_06$PostW <- as.factor(train2003_06$PostW)
# 
# # Construct the formula
# f_2003_06 <- formula(paste("PostW ~", paste(colnames(train_numeric_03_06), collapse = "+")))
# 
# # Train neural network
# nn1_2003_06 <- neuralnet(f_2003_06, data = train2003_06, hidden = 3, act.fct = "logistic", linear.output = FALSE)

```

```{r}
# result=compute(nn1_2003_06, test2003_06)
# result$net.result
```




### Random Forest Model
```{r}
library(randomForest)
set.seed(2003)
RF <- randomForest(PostW ~., data=train,
                   ntree = 1000,  # number of trees
                   importance = TRUE)  # allows you to track variable importance

print(RF)
plot(RF)  # OOB error is OOB MISC (in black)
```
OOB Estimate of Error Rate: 61.07%

```{r}
# Plot error rate
plot(RF$err.rate[,1], type="l", col="black", ylim = c(0.2,1), ylab="Error Rate", xlab="Number of Trees", main="RF Error Rate Plot") # OOB
lines(RF$err.rate[,2], col="red") # First Round Exit
lines(RF$err.rate[,3], col="orange") # Round of 32
lines(RF$err.rate[,4], col="darkgreen") # Sweet 16
lines(RF$err.rate[,5], col="blue") # Elite Eight
lines(RF$err.rate[,6], col="purple") # Final 4
lines(RF$err.rate[,7], col="maroon") #Runner up
lines(RF$err.rate[,8], col="darkblue") #champ
legend("topright", legend=c("Champion", "Runner Up", "Final Four", "Elite Eight", "First Round Exit", "Sweet Sixteen", "Out Of Bag Error", "Round of Thirty Two"), col=c("darkblue", "maroon", "purple", "blue", "red", "darkgreen", "black", "orange"), lty=1)
```


```{r}
y_actual_rf <- test$PostW

# Predict using the trained model
y_pred_rf <- predict(RF, newdata = test)

# Create a confusion matrix
conf_matrix_rf <- confusionMatrix(y_pred_rf, y_actual_rf)
conf_matrix_rf
```

```{r}
rf_pred <- as.ordered(y_pred_rf)
roc_curve_rf <- multiclass.roc(test$PostW, rf_pred)
roc_curve_rf
```
AUC: 0.6283


### Multiclass ROC Index

```{r}
true_label <- dummy::dummy(test)
true_label <- data.frame(true_label)
colnames(true_label) <- paste(colnames(true_label), "_true")
final_df <- cbind(true_label, pred_matrix_jk, pred_prob_tree, reg.step_pred, rf_pred)
```


```{r}
# Assuming 'final_df' contains the predicted probabilities for each class and true labels are now factors
roc_res <- multi_roc(final_df[, c("First.Round.Exit", "Round.of.Thirty.Two", "Sweet.Sixteen", "Elite.Eight", "Final.Four", "Runner.Up", "Champion")], force_diag = TRUE)
pr_res <- multi_pr(final_df[, c("First.Round.Exit", "Round.of.Thirty.Two", "Sweet.Sixteen", "Elite.Eight", "Final.Four", "Runner.Up", "Champion")], force_diag = TRUE)
```

```{r}
plot_roc_df <- plot_roc_data(roc_res)
plot_pr_df <- plot_pr_data(pr_res)
```



### Final Predictions
want to use "bottom up" approach; predict champions first, then runners up, etc -> even if x team has higher probability for 5 than 6, choose 6 if its the team with the highest 6 probability

wont alter actual models, will just have to design some algorithm / formula when applying model to test data (one specific year)

**Reminder that the teams in this data have already advanced to Round of 32, we are predicting past this** - maybe just predict elite 8, final 4 ?

Use Jackknife - LOOCV
```{r}
multiclass_03 <- multiclass_data %>% 
  filter(Season == 2003)
```


```{r}
multiclass_03_subset <- multiclass_03[, colnames(train)]

# Assuming multiclass_03 has a column named 'team_name'
team_name_column <- multiclass_03$Team_Name

# Combine the relevant columns from multiclass_03 and team_name_column
multiclass_03_subset <- cbind(Team_Name = team_name_column, multiclass_03_subset)

# Assuming 'team_name' is the column you want to use as row names
row_names_03 <- multiclass_03_subset$Team_Name

# Set 'team_name' as row names
rownames(multiclass_03_subset) <- row_names_03

# Predict using the subsetted data
multiclass_03_subset$predictions_jk <- predict(RF, newdata = multiclass_03_subset, type = "prob")

multiclass_03_subset <- multiclass_03_subset %>% 
  mutate(predictions_jk = as.data.frame(predictions_jk))
```

```{r}
# Create an empty column for predicted_PostW
multiclass_03_subset$predicted_PostW <- NA

# Identify the team with the highest probability for Champion
champion_index <- which.max(multiclass_03_subset$predictions_jk$Champion)

# Assign predicted_PostW for Champion
multiclass_03_subset$predicted_PostW[champion_index] <- "Champion"

# Exclude the row with the highest probability for Champion
other_rows_champ <- setdiff(1:nrow(multiclass_03_subset), champion_index)


# Identify the top 1 team with the highest probability for Runner Up among remaining rows
runner_up_index <- multiclass_03_subset %>%
  slice(other_rows_champ) %>%
  arrange(desc(predictions_jk$Runner.Up)) %>%
  slice_head(n = 1)

runner_up_row_number <- which(rownames(multiclass_03_subset) %in% rownames(runner_up_index))

# Assign predicted_PostW for Runner.Up
multiclass_03_subset$predicted_PostW[runner_up_row_number] <- "Runner Up"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_runnerup <- setdiff(1:nrow(multiclass_03_subset), c(champion_index, runner_up_row_number))


# Identify the top 2 teams with the highest probability for Final Four among remaining rows
final_four_index <- multiclass_03_subset %>%
  slice(other_rows_runnerup) %>%
  arrange(desc(predictions_jk$Final.Four)) %>%
  slice(1:2)

final_four_row_numbers <- which(rownames(multiclass_03_subset) %in% rownames(final_four_index))

# Assign predicted_PostW for Final.Four
multiclass_03_subset$predicted_PostW[final_four_row_numbers] <- "Final Four"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_final_four <- setdiff(1:nrow(multiclass_03_subset), c(champion_index, runner_up_row_number, final_four_row_numbers))


# Identify the top 4 teams with the highest probability for Elite Eight among remaining rows
elite_eight_index <- multiclass_03_subset %>%
  slice(other_rows_final_four) %>%
  arrange(desc(predictions_jk$Elite.Eight)) %>%
  slice(1:4)

elite_eight_row_numbers <- which(rownames(multiclass_03_subset) %in% rownames(elite_eight_index))

# Assign predicted_PostW for Final.Four
multiclass_03_subset$predicted_PostW[elite_eight_row_numbers] <- "Elite Eight"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_elite_eight <- setdiff(1:nrow(multiclass_03_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers))


# Identify the top 8 teams with the highest probability for Sweet Sixteen among remaining rows
sweet_sixteen_index <- multiclass_03_subset %>%
  slice(other_rows_elite_eight) %>%
  arrange(desc(predictions_jk$Sweet.Sixteen)) %>%
  slice(1:8)

sweet_sixteen_row_numbers <- which(rownames(multiclass_03_subset) %in% rownames(sweet_sixteen_index))

# Assign predicted_PostW for Final.Four
multiclass_03_subset$predicted_PostW[sweet_sixteen_row_numbers] <- "Sweet Sixteen"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_sweet_sixteen <- setdiff(1:nrow(multiclass_03_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers))


# Identify the top 16 teams with the highest probability for Round of 32 among remaining rows
round_of_thirty_two_index <- multiclass_03_subset %>%
  slice(other_rows_sweet_sixteen) %>%
  arrange(desc(predictions_jk$Round.of.Thirty.Two)) %>%
  slice(1:8)

round_of_thirty_two_row_numbers <- which(rownames(multiclass_03_subset) %in% rownames(round_of_thirty_two_index))

# Assign predicted_PostW for Final.Four
multiclass_03_subset$predicted_PostW[round_of_thirty_two_row_numbers] <- "Round of Thirty Two"


# Display the result
multiclass_03_subset[, c("PostW", "predicted_PostW")] %>% 
  mutate(predicted_PostW = factor(predicted_PostW, levels = c("First Round Exit", "Round of Thirty Two", "Sweet Sixteen", "Elite Eight", "Final Four", "Runner Up", "Champion"), ordered = T)) %>% 
  arrange(desc(predicted_PostW))
```
Initially was doing highest prob of champ to champ, highest runner up excluding champ team to runner up, and so on, but the issue was that, for example, Syracuse ended up with predicted PostW of Round of 32 since its Champion prob was so high and others were lower



```{r}
multiclass_08 <- multiclass_data %>% 
  filter(Season == 2008)
```

```{r}
multiclass_08_subset <- multiclass_08[, colnames(train)]

# Assuming multiclass_03 has a column named 'team_name'
team_name_column <- multiclass_08$Team_Name

# Combine the relevant columns from multiclass_03 and team_name_column
multiclass_08_subset <- cbind(Team_Name = team_name_column, multiclass_08_subset)

# Assuming 'team_name' is the column you want to use as row names
row_names_08 <- multiclass_08_subset$Team_Name

# Set 'team_name' as row names
rownames(multiclass_08_subset) <- row_names_08

# Predict using the subsetted data
multiclass_08_subset$predictions_jk <- predict(RF, newdata = multiclass_08_subset, type = "prob")

multiclass_08_subset <- multiclass_08_subset %>% 
  mutate(predictions_jk = as.data.frame(predictions_jk))
```

```{r}
# Create an empty column for predicted_PostW
multiclass_08_subset$predicted_PostW <- NA

# Identify the team with the highest probability for Champion
champion_index <- which.max(multiclass_08_subset$predictions_jk$Champion)

# Assign predicted_PostW for Champion
multiclass_08_subset$predicted_PostW[champion_index] <- "Champion"

# Exclude the row with the highest probability for Champion
other_rows_champ <- setdiff(1:nrow(multiclass_08_subset), champion_index)


# Identify the top 1 team with the highest probability for Runner Up among remaining rows
runner_up_index <- multiclass_08_subset %>%
  slice(other_rows_champ) %>%
  arrange(desc(predictions_jk$Runner.Up)) %>%
  slice_head(n = 1)

runner_up_row_number <- which(rownames(multiclass_08_subset) %in% rownames(runner_up_index))

# Assign predicted_PostW for Runner.Up
multiclass_08_subset$predicted_PostW[runner_up_row_number] <- "Runner Up"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_runnerup <- setdiff(1:nrow(multiclass_08_subset), c(champion_index, runner_up_row_number))


# Identify the top 2 teams with the highest probability for Final Four among remaining rows
final_four_index <- multiclass_08_subset %>%
  slice(other_rows_runnerup) %>%
  arrange(desc(predictions_jk$Final.Four)) %>%
  slice(1:2)

final_four_row_numbers <- which(rownames(multiclass_08_subset) %in% rownames(final_four_index))

# Assign predicted_PostW for Final.Four
multiclass_08_subset$predicted_PostW[final_four_row_numbers] <- "Final Four"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_final_four <- setdiff(1:nrow(multiclass_08_subset), c(champion_index, runner_up_row_number, final_four_row_numbers))


# Identify the top 4 teams with the highest probability for Elite Eight among remaining rows
elite_eight_index <- multiclass_08_subset %>%
  slice(other_rows_final_four) %>%
  arrange(desc(predictions_jk$Elite.Eight)) %>%
  slice(1:4)

elite_eight_row_numbers <- which(rownames(multiclass_08_subset) %in% rownames(elite_eight_index))

# Assign predicted_PostW for Final.Four
multiclass_08_subset$predicted_PostW[elite_eight_row_numbers] <- "Elite Eight"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_elite_eight <- setdiff(1:nrow(multiclass_08_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers))


# Identify the top 8 teams with the highest probability for Sweet Sixteen among remaining rows
sweet_sixteen_index <- multiclass_08_subset %>%
  slice(other_rows_elite_eight) %>%
  arrange(desc(predictions_jk$Sweet.Sixteen)) %>%
  slice(1:8)

sweet_sixteen_row_numbers <- which(rownames(multiclass_08_subset) %in% rownames(sweet_sixteen_index))

# Assign predicted_PostW for Final.Four
multiclass_08_subset$predicted_PostW[sweet_sixteen_row_numbers] <- "Sweet Sixteen"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_sweet_sixteen <- setdiff(1:nrow(multiclass_08_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers))


# Identify the top 16 teams with the highest probability for Round of 32 among remaining rows
round_of_thirty_two_index <- multiclass_08_subset %>%
  slice(other_rows_sweet_sixteen) %>%
  arrange(desc(predictions_jk$Round.of.Thirty.Two)) %>%
  slice(1:16)

round_of_thirty_two_row_numbers <- which(rownames(multiclass_08_subset) %in% rownames(round_of_thirty_two_index))

# Assign predicted_PostW for Final.Four
multiclass_08_subset$predicted_PostW[round_of_thirty_two_row_numbers] <- "Round of Thirty Two"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_round_of_thirty_two <- setdiff(1:nrow(multiclass_08_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers, round_of_thirty_two_row_numbers))


# Identify the top 32 teams with the highest probability for Round of 32 among remaining rows
first_round_exit_index <- multiclass_08_subset %>%
  slice(other_rows_round_of_thirty_two) %>%
  arrange(desc(predictions_jk$First.Round.Exit)) %>%
  slice(1:32)

first_round_exit_row_numbers <- which(rownames(multiclass_08_subset) %in% rownames(first_round_exit_index))

# Assign predicted_PostW for Final.Four
multiclass_08_subset$predicted_PostW[first_round_exit_row_numbers] <- "First Round Exit"


# Display the result
multiclass_08_subset[, c("PostW", "predicted_PostW")] %>% 
  mutate(predicted_PostW = factor(predicted_PostW, levels = c("First Round Exit", "Round of Thirty Two", "Sweet Sixteen", "Elite Eight", "Final Four", "Runner Up", "Champion"), ordered = T)) %>% 
  arrange(desc(predicted_PostW))
```


```{r}
multiclass_16 <- multiclass_data %>% 
  filter(Season == 2016)
```

```{r}
multiclass_16_subset <- multiclass_16[, colnames(train)]

# Assuming multiclass_03 has a column named 'team_name'
team_name_column <- multiclass_16$Team_Name

# Combine the relevant columns from multiclass_03 and team_name_column
multiclass_16_subset <- cbind(Team_Name = team_name_column, multiclass_16_subset)

# Assuming 'team_name' is the column you want to use as row names
row_names_16 <- multiclass_16_subset$Team_Name

# Set 'team_name' as row names
rownames(multiclass_16_subset) <- row_names_16

# Predict using the subsetted data
multiclass_16_subset$predictions_jk <- predict(RF, newdata = multiclass_16_subset, type = "prob")

multiclass_16_subset <- multiclass_16_subset %>%
  mutate(predictions_jk = as.data.frame(predictions_jk))
```

```{r}
# Create an empty column for predicted_PostW
multiclass_16_subset$predicted_PostW <- NA

# Identify the team with the highest probability for Champion
champion_index <- which.max(multiclass_16_subset$predictions_jk$Champion)

# Assign predicted_PostW for Champion
multiclass_16_subset$predicted_PostW[champion_index] <- "Champion"

# Exclude the row with the highest probability for Champion
other_rows_champ <- setdiff(1:nrow(multiclass_16_subset), champion_index)


# Identify the top 1 team with the highest probability for Runner Up among remaining rows
runner_up_index <- multiclass_16_subset %>%
  slice(other_rows_champ) %>%
  arrange(desc(predictions_jk$Runner.Up)) %>%
  slice_head(n = 1)

runner_up_row_number <- which(rownames(multiclass_16_subset) %in% rownames(runner_up_index))

# Assign predicted_PostW for Runner.Up
multiclass_16_subset$predicted_PostW[runner_up_row_number] <- "Runner Up"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_runnerup <- setdiff(1:nrow(multiclass_16_subset), c(champion_index, runner_up_row_number))


# Identify the top 2 teams with the highest probability for Final Four among remaining rows
final_four_index <- multiclass_16_subset %>%
  slice(other_rows_runnerup) %>%
  arrange(desc(predictions_jk$Final.Four)) %>%
  slice(1:2)

final_four_row_numbers <- which(rownames(multiclass_16_subset) %in% rownames(final_four_index))

# Assign predicted_PostW for Final.Four
multiclass_16_subset$predicted_PostW[final_four_row_numbers] <- "Final Four"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_final_four <- setdiff(1:nrow(multiclass_16_subset), c(champion_index, runner_up_row_number, final_four_row_numbers))


# Identify the top 4 teams with the highest probability for Elite Eight among remaining rows
elite_eight_index <- multiclass_16_subset %>%
  slice(other_rows_final_four) %>%
  arrange(desc(predictions_jk$Elite.Eight)) %>%
  slice(1:4)

elite_eight_row_numbers <- which(rownames(multiclass_16_subset) %in% rownames(elite_eight_index))

# Assign predicted_PostW for Final.Four
multiclass_16_subset$predicted_PostW[elite_eight_row_numbers] <- "Elite Eight"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_elite_eight <- setdiff(1:nrow(multiclass_16_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers))


# Identify the top 8 teams with the highest probability for Sweet Sixteen among remaining rows
sweet_sixteen_index <- multiclass_16_subset %>%
  slice(other_rows_elite_eight) %>%
  arrange(desc(predictions_jk$Sweet.Sixteen)) %>%
  slice(1:8)

sweet_sixteen_row_numbers <- which(rownames(multiclass_16_subset) %in% rownames(sweet_sixteen_index))

# Assign predicted_PostW for Final.Four
multiclass_16_subset$predicted_PostW[sweet_sixteen_row_numbers] <- "Sweet Sixteen"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_sweet_sixteen <- setdiff(1:nrow(multiclass_16_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers))


# Identify the top 16 teams with the highest probability for Round of 32 among remaining rows
round_of_thirty_two_index <- multiclass_16_subset %>%
  slice(other_rows_sweet_sixteen) %>%
  arrange(desc(predictions_jk$Round.of.Thirty.Two)) %>%
  slice(1:16)

round_of_thirty_two_row_numbers <- which(rownames(multiclass_16_subset) %in% rownames(round_of_thirty_two_index))

# Assign predicted_PostW for Final.Four
multiclass_16_subset$predicted_PostW[round_of_thirty_two_row_numbers] <- "Round of Thirty Two"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_round_of_thirty_two <- setdiff(1:nrow(multiclass_16_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers, round_of_thirty_two_row_numbers))


# Identify the top 32 teams with the highest probability for Round of 32 among remaining rows
first_round_exit_index <- multiclass_16_subset %>%
  slice(other_rows_round_of_thirty_two) %>%
  arrange(desc(predictions_jk$First.Round.Exit)) %>%
  slice(1:32)

first_round_exit_row_numbers <- which(rownames(multiclass_16_subset) %in% rownames(first_round_exit_index))

# Assign predicted_PostW for Final.Four
multiclass_16_subset$predicted_PostW[first_round_exit_row_numbers] <- "First Round Exit"


# Display the result
multiclass_16_subset[, c("PostW", "predicted_PostW")] %>% 
  mutate(predicted_PostW = factor(predicted_PostW, levels = c("First Round Exit", "Round of Thirty Two", "Sweet Sixteen", "Elite Eight", "Final Four", "Runner Up", "Champion"), ordered = T)) %>% 
  arrange(desc(predicted_PostW))
```


#### 2020 Tournament

A second question this project will aim to answer is if the 2019-2020 season were to have run uninterrupted, how would the tournament have unfolded and who would have been the eventual champion? (add to end of first paragraph in paper)

Finally, once the model creation is final, it will be implemented on the 2019-2020 regular season in order to predict the 2020 NCAA Tournament and its eventual champion.

using a manually created bracket fulfilling the necessary criteria. (add to end of final paragraph of introduction)

```{r}
fulldata_2020$predictions_binary <- predict(RF_binary, newdata = fulldata_2020, type = "response")

# If you want to filter rows where PostW_binary = 1
multiclass_20 <- fulldata_2020[fulldata_2020$predictions_binary == "level_1", ]

multiclass_20_subset <- multiclass_20[, colnames(train)]

# Assuming multiclass_03 has a column named 'team_name'
team_name_column <- multiclass_20$Team_Name

# Combine the relevant columns from multiclass_03 and team_name_column
multiclass_20_subset <- cbind(Team_Name = team_name_column, multiclass_20_subset)

# Assuming 'team_name' is the column you want to use as row names
row_names_20 <- multiclass_20_subset$Team_Name

# Set 'team_name' as row names
rownames(multiclass_20_subset) <- row_names_20

# Predict using the subsetted data
multiclass_20_subset$predictions_jk <- predict(RF, newdata = multiclass_20_subset, type = "prob")

multiclass_20_subset <- multiclass_20_subset %>%
  mutate(predictions_jk = as.data.frame(predictions_jk))

multiclass_20_subset$predictions_jk %>% 
  arrange(desc(Champion))
```

```{r}
# Create an empty column for predicted_PostW
multiclass_20_subset$predicted_PostW <- NA

# Identify the team with the highest probability for Champion
champion_index <- which.max(multiclass_20_subset$predictions_jk$Champion)

# Assign predicted_PostW for Champion
multiclass_20_subset$predicted_PostW[champion_index] <- "Champion"

# Exclude the row with the highest probability for Champion
other_rows_champ <- setdiff(1:nrow(multiclass_20_subset), champion_index)


# Identify the top 1 team with the highest probability for Runner Up among remaining rows
runner_up_index <- multiclass_20_subset %>%
  slice(other_rows_champ) %>%
  arrange(desc(predictions_jk$Runner.Up)) %>%
  slice_head(n = 1)

runner_up_row_number <- which(rownames(multiclass_20_subset) %in% rownames(runner_up_index))

# Assign predicted_PostW for Runner.Up
multiclass_20_subset$predicted_PostW[runner_up_row_number] <- "Runner Up"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_runnerup <- setdiff(1:nrow(multiclass_20_subset), c(champion_index, runner_up_row_number))


# Identify the top 2 teams with the highest probability for Final Four among remaining rows
final_four_index <- multiclass_20_subset %>%
  slice(other_rows_runnerup) %>%
  arrange(desc(predictions_jk$Final.Four)) %>%
  slice(1:2)

final_four_row_numbers <- which(rownames(multiclass_20_subset) %in% rownames(final_four_index))

# Assign predicted_PostW for Final.Four
multiclass_20_subset$predicted_PostW[final_four_row_numbers] <- "Final Four"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_final_four <- setdiff(1:nrow(multiclass_20_subset), c(champion_index, runner_up_row_number, final_four_row_numbers))


# Identify the top 4 teams with the highest probability for Elite Eight among remaining rows
elite_eight_index <- multiclass_20_subset %>%
  slice(other_rows_final_four) %>%
  arrange(desc(predictions_jk$Elite.Eight)) %>%
  slice(1:4)

elite_eight_row_numbers <- which(rownames(multiclass_20_subset) %in% rownames(elite_eight_index))

# Assign predicted_PostW for Final.Four
multiclass_20_subset$predicted_PostW[elite_eight_row_numbers] <- "Elite Eight"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_elite_eight <- setdiff(1:nrow(multiclass_20_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers))


# Identify the top 8 teams with the highest probability for Sweet Sixteen among remaining rows
sweet_sixteen_index <- multiclass_20_subset %>%
  slice(other_rows_elite_eight) %>%
  arrange(desc(predictions_jk$Sweet.Sixteen)) %>%
  slice(1:8)

sweet_sixteen_row_numbers <- which(rownames(multiclass_20_subset) %in% rownames(sweet_sixteen_index))

# Assign predicted_PostW for Final.Four
multiclass_20_subset$predicted_PostW[sweet_sixteen_row_numbers] <- "Sweet Sixteen"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_sweet_sixteen <- setdiff(1:nrow(multiclass_20_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers))


# Identify the top 16 teams with the highest probability for Round of 32 among remaining rows
round_of_thirty_two_index <- multiclass_20_subset %>%
  slice(other_rows_sweet_sixteen) %>%
  arrange(desc(predictions_jk$Round.of.Thirty.Two)) %>%
  slice(1:16)

round_of_thirty_two_row_numbers <- which(rownames(multiclass_20_subset) %in% rownames(round_of_thirty_two_index))

# Assign predicted_PostW for Final.Four
multiclass_20_subset$predicted_PostW[round_of_thirty_two_row_numbers] <- "Round of Thirty Two"

# Exclude the row with the highest probability for Champion, Runner Up
other_rows_round_of_thirty_two <- setdiff(1:nrow(multiclass_20_subset), c(champion_index, runner_up_row_number, final_four_row_numbers, elite_eight_row_numbers, sweet_sixteen_row_numbers, round_of_thirty_two_row_numbers))


# Identify the top 32 teams with the highest probability for Round of 32 among remaining rows
first_round_exit_index <- multiclass_20_subset %>%
  slice(other_rows_round_of_thirty_two) %>%
  arrange(desc(predictions_jk$First.Round.Exit)) %>%
  slice(1:32)

first_round_exit_row_numbers <- which(rownames(multiclass_20_subset) %in% rownames(first_round_exit_index))

# Assign predicted_PostW for Final.Four
multiclass_20_subset$predicted_PostW[first_round_exit_row_numbers] <- "First Round Exit"


# Display the result
multiclass_20_subset[, c("PostW", "predicted_PostW")] %>% 
  mutate(predicted_PostW = factor(predicted_PostW, levels = c("First Round Exit", "Round of Thirty Two", "Sweet Sixteen", "Elite Eight", "Final Four", "Runner Up", "Champion"), ordered = T)) %>% 
  arrange(desc(predicted_PostW)) %>% 
  dplyr::select(predicted_PostW)
```

